NURM: a tool to locate numerical differences in pipelines

### 2019-05-27 paper.tex
Some updates

\section{Tool description}

@@

\subsection{Provenance capture and representation}

We use the \reprozip tool~\cite{Chirigati2016} to record: (1) 
the tree of processes executed by the pipeline and (2) the list of 
files read and written by each process. This information is collected 
by system call interceptions, through the \texttt{ptrace} Unix system 
call, and stored in a \texttt{SQLite} database. The database stores 
information of all the processes which are created by the 
\texttt{clone()} or \texttt{fork()} system calls. It also records the 
files opened by each process (in read, write or execution mode), 
including the result files and the temporary files.

NURM-tool reconstructs the tree of processes starting from the first 
process created by the pipeline and through identifying its child 
processes as the ones that were created through \texttt{clone()} or 
\texttt{fork()}. It creates a process graph from this tree by adding 
edges corresponding to file dependencies between processes. A file 
dependency is defined between processes A and B if a file written by A 
is read by B. Figure~\ref{fig:simple_script} shows an example of a 
process tree constructed for the simple bash script illustrated in 
Algorithm~\ref{algo:sample-script} from the brain extraction procedure.

\begin{algorithm}[h!]
\caption{Sample script from brain extraction process}
\label{algo:sample-script}
\begin{verbatim}
#!/bin/bash
if [ # !=1 ]
then
    echo "usage: 0 <inputimage.nii.gz>"
    exit 1
fi
input_image=$1
bet_output="$(basename ${input_image} 
                       .nii.gz)_brain.nii.gz"
bet_output_binarized="$(basename ${input_image} 
                       .nii.gz)_brain_bin.nii.gz"

bet ${input_image} ${bet_output} > bet_temp.out
echo "Voxels / Volume in brain mask:"
fslstats ${bet_output} -V
fslmaths ${bet_output} ${bet_output_binarized}
echo "Voxels / Volum in binarized brain mask:"
\rm bet_temp.out
\end{verbatim}
\end{algorithm}

\begin{figure}
\centering
  \includegraphics[scale=0.25]{images/simple_graph}
  \caption{Process tree constructed from an example brain extraction
	script. Every node in the graph is labeled using (1) a process id 
	created by our reconstruction, (2) the name of the executable run 
	by the process. Processes that read or write temporary files are 
	represented with squares; other ones with circles. Plain edges 
	represent the process tree (\texttt{fork()} or \texttt{clone()} 
	system calls). Dashed edges represent file dependencies: temporary 
	files are in yellow and result files are in green.}
  \label{fig:simple_script}
\end{figure}

\subsection{Subject type}

>>>>

\tristan{define subjects, explain neuroimaging, bring context.}
\section{Tool description}

@@

\subsection{Provenance capture and representation}
\tristan{All these sections should refer to labels on Figure 1.}

We use \reprozip~\cite{Chirigati2016} to record: (1) 
the tree of processes executed by the pipeline and (2) the list of 
files read and written by each process. This information is collected 
by \reprozip through the \texttt{ptrace} Unix system 
call, and stored in a \texttt{SQLite} database. The database stores 
information of all the processes which are created by the 
\texttt{clone()} or \texttt{fork()} system calls. It also records the 
files opened by each process (in read, write or execution mode), 
including result files and temporary files.

Our tool reconstructs the tree of processes starting from the first process
created by the pipeline and traversing the tree through occurrences of
\texttt{clone()} and \texttt{fork()}. It also creates a process
\emph{graph} from this tree by adding edges corresponding to file
dependencies between processes. A file dependency is defined between
processes A and B if a file written by A 
is read by B. Figure~\ref{fig:simple_script} shows an example of a 
process tree and graph constructed from the example pipeline in
Listing~\ref{listing:sample-script}.
\begin{listing}
\begin{minted}[frame=single,
  framesep=3mm,
  linenos=false,
  xleftmargin=0pt,
  tabsize=4]{bash}
#!/bin/bash
if [ #$ !=1 ]
then
    echo "usage: 0 <inputimage.nii.gz>"
    exit 1
fi

# Parse argument, set file names
input_image=$1
bet_output="$(basename ${input_image} 
                       .nii.gz)_brain.nii.gz"
bet_output_binarized="$(basename ${input_image} 
                       .nii.gz)_brain_bin.nii.gz"

# Run FSL bet, put result ${bet_output}
bet ${input_image} ${bet_output} > bet_temp.out
echo "Voxels / Volume in brain mask:"
# Run FSL stats on ${bet_output}
fslstats ${bet_output} -V
# Run FSL maths on ${bet_output}
fslmaths ${bet_output} ${bet_output_binarized}
echo "Voxels / Volume in binarized brain mask:"

\rm bet_temp.out
\end{minted}
  \caption{Example pipeline}
  \label{listing:sample-script}
\end{listing}

\begin{figure}
\centering
  \includegraphics[scale=0.25]{images/simple_graph}
  \caption{Process tree and graph
  constructed from the example pipeline in
  Listing~\ref{listing:sample-script}.
  Processes that read or write
  temporary files are 
  represented with squares. Plain edges 
  represent the process tree (\texttt{fork()} or \texttt{clone()} 
  system calls). Dashed edges represent file dependencies: temporary 
  files are in yellow and result files are in green.
  Every node in the tree is labeled using (1) a process id created by our
  reconstruction, (2) the name of the executable run by the process.
  Process 0 is the initial call to the \texttt{bash} interpreter, and
  processes 1, 3 and 4 are the calls to FSL bet, stats and maths made in
  Listing~\ref{listing:sample-script}. Process 2 is forked by process 1: it
  was captured by \reprozip while it did not appear in
  Listing~\ref{listing:sample-script}. \tristan{The script has only 1 call to fslstats, this should be fixed.}
}
  \label{fig:simple_script}
\end{figure}

\subsection{Subject types}

Different subjects may lead to different process trees and graphs, due to
variations in the processing pipeline. Such variations may be coming from differences
in data types or cardinality, for instance, some subj
